---
title: "HERE IS THE TITLE OF MY ABSTRACT"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, cache=FALSE, echo=FALSE}
library(rmarkdown)
```


Authors: John H. Curry^1^, Kathy S. James^1^, Patrick S. Curry^1^ 

\newline

Affiliations: ^1^University of Michigan  

\newline  \newline

*Presenting author information*  
Name: John H. Curry  
Email: curry@umed.edu  
Affiliation details: Kinesiology, University of Somewhere, Ottawa, Canada  

\newline \newline

*Coauthor #2*  
Name: Kathy S. James  
Email: james@umed.edu   
Affiliation details: Kinesiology, University of Somewhere, Ottawa, Canada  

\newline \newline

*Coauthor #3*  
Name: Patrick S. Curry  
Email: curry2@umed.edu  
Affiliation details: Kinesiology, University of Somewhere, Ottawa, Canada  

\newline \newline

## Introduction
Here is where I write my introduction....

\newline \newline

## Methods
Here is where I write my methods

\newline \newline


## Results
Here is where I write my results..