---
title: "XueModules"
author: "Giuliano Netto Flores Cruz"
date: "September 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(echo = TRUE, root.dir = '/home/giulianonetto/windows/tcc/checklist/genesigs/papers/Xue, 2014')
library(DT)
```
# Modules from Xue, 2014.
9498 unique present genes were clustered into 49 modules. 
M1-, M2- and TPP-associated modules are 7-9, 13-15, and 30, 32-33, respecitively.

```{r echo=FALSE}

library(stringr)
dat <- read.table('modules.csv', sep = '\t', header = T, stringsAsFactors = F)

dat_colnames <- colnames(dat)
dat_colnames_new = vector()
for (i in 1:ncol(dat)){
  old <- str_extract(dat_colnames[i], "[0-9]+")
  new = paste0("Module", old)
  dat_colnames_new = c(dat_colnames_new, new)
}
colnames(dat) <- dat_colnames_new

datatable(dat, rownames = FALSE, filter = 'top',
          caption = "Table 1. Modules defined by Xue, 2014.",
          options=list(pageLength = 100, scrollX='400px', scrollY='400px',
          lengthMenu = c(30, 100, 1000) 

  )
)
```

List of Genes used for the 49 modules defined by Xue, 2014. Human gene symbols were converted to the respective mouse orthologues by combining information from Ensembl BioMart ( http://www.ensembl.org/biomart/martview ) using the species specific gene symbols and Ensembl Gene IDs.. For some of the genes BioGPS (http://biogps.org/#goto=welcome) was used if no orthologue was found in BioMart

```{r echo=FALSE}
uq_elem=c()
for(i in 1:ncol(dat))
{
  uq_elem=c(unique(dat[,i]), uq_elem)
  uq_elem=unique(uq_elem)
}
genes_list <- data.frame('GeneSymbols' =uq_elem)

datatable(genes_list, filter = 'top',
          caption = "Table 2. Genes included in modules by Xue, 2014.",
          options=list(pageLength = 100, scrollX='400px', scrollY='400px',
          lengthMenu = c(30, 100, 1000)))
```
